---
title: "HW3"
author: "Seraphym Ignacio"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

ID: sri346\
\
GitHub Link:

```{r echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}
# setup (just in case)
library(tidyverse)
library(rvest)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(knitr)
library(lubridate)
library(mosaic)
```

# Problem 1

```{r echo=FALSE}
# q1
gasprices <- read.csv("gasprices.csv")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# theory a: gas stations charge more if they lack direct competition in sight

mean(Price ~ Competitors, data = gasprices)
diffmean(Price ~ Competitors, data = gasprices)

boot_comp = do(10000) * diffmean(Price ~ Competitors, data=mosaic::resample(gasprices))

ggplot(boot_comp) + 
  geom_histogram(aes(x = diffmean))

confint(boot_comp, level = 0.95)
```

## Theory A:

-   [Claim]{.underline}: Gas stations charge more if they lack direct competition in sight.

-   [Evidence]{.underline}: Gas stations with no competitors have prices \$0.023 cents higher than gas stations with competitors. Compared to a wider population, this data was taken from 101 gas stations, so there is some uncertainty with these observations.

-   [Conclusion]{.underline}: With a 95% confidence, and ruling out a difference of zero, it can be stated that gas stations with no competitors do not have significantly higher prices than ones with competitors on average, with a difference of \$0.007-\$0.06 in mean values, which does not support Theory A.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# theory b

cor(Price ~ Income, data = gasprices)

boot_income = do(10000) * cor(Price ~ Income, data = mosaic::resample(gasprices))

ggplot(boot_income) + 
  geom_histogram(aes(x = cor))
```

## Theory B:

-   [Claim]{.underline}: The richer the area, the higher the gas prices.

-   [Evidence]{.underline}: The correlation between gas prices and income is 0.40, which represents a moderately positive relationship between the two observed variables. Again, all observations are said with some uncertainty as there were only 101 out of the many gas stations in the population.

-   [Conclusion]{.underline}: With 95% confidence and ruling out a difference of zero, there is a correlation of 0.57-0.20 between gas prices and area income. This positive relationship suggests that higher-income areas tend to have higher gas prices and supports Theory B.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# theory c

mean(Price ~ Stoplight, data = gasprices)
diffmean(Price ~ Stoplight, data = gasprices)

boot_stoplight = do(10000) * diffmean(Price ~ Stoplight, data = mosaic::resample(gasprices))

ggplot(boot_stoplight) + 
  geom_histogram(aes(x = diffmean))

confint(boot_stoplight, level = 0.95)
```

## Theory C:

-   Claim: Gas stations at stoplights charge more.

-   Evidence: Gas stations with no stoplights have prices of \$0.003 higher than gas stations with stoplights. This observation comes with some uncertainty due to taking a small part of the population.

-   Conclusion: This data does not rule out a difference of zero, and so it can be verified that the data supports Theory A and the average price between these types of gas stations are not statistically significant.

```{r echo=FALSE}
#theory d
```

## Theory D:

-   Claim: Gas stations with direct highway access charge more.

-   Evidence:

-   Conclusion:

```{r echo=FALSE}
# theory e
```

## Theory E:

-   Claim: Shell charges more than all other non-Shell brands.

-   Evidence:

-   Conclusion:

# Problem 2

```{r echo=FALSE}
# q2
sclass <- read.csv("sclass.csv")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# part a

cars116 <- sclass |>
  filter(year == "2011", trim == "63 AMG")


boot_mile <- do(10000) * mean(~mileage, data = mosaic::resample(cars116))

boot_mile |>
  summarize(std_err_ = sd(mean))

ggplot(boot_mile) + 
  geom_histogram(aes(x= mean))

confint(boot_mile, level = 0.95)
```

## Part A

Based on these 116 cars from a 30,000-car dataset, it can be stated with 95% confidence that the average mileage of the 2011 S-Class 63 AMGs is 26.5 thousand. The true average mileage would be expected to fall between approximately 26 thousand and 32 thousand.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# part b

cars2889 <- sclass |>
  filter(year == "2014", trim == "550") |>
  mutate(isBlack = color == "Black")

boot_black <- do(10000) * mean(~isBlack, data = mosaic::resample(cars2889))

boot_black |>
  summarize(std_err_ = sd(mean))

ggplot(boot_black) + 
  geom_histogram(aes(x= mean))

confint(boot_black, level = 0.95)
```

## Part B

Based on these 2889 cars from a 30,000-car dataset, it can be stated with 95% confidence that the average amount of cars painted black of the 2014 S-Class 550s is 0.43. The true average amount would be expected to fall between approximately 0.42 and 0.45.

# Problem 3

```{r echo=FALSE}
# q3
nbc <- read.csv("nbc_pilotsurvey.csv")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# part a

edVearl <- nbc |>
  filter(Show %in% c("Living with Ed", "My Name is Earl"))

boot_edVearl <- do(10000) * mean(~Q1_Happy, data = mosaic::resample(edVearl))

boot_edVearl |>
  summarize(std_err_ = sd(mean))

ggplot(boot_edVearl) + 
  geom_histogram(aes(x= mean))

confint(boot_edVearl, level=0.95)
```

## Part A

1.  Question: Who makes people happier: Ed or earl?
2.  Approach: To answer this question, I used viewer responses from the dataset for two shows called "Living with Ed" and "My Name is Earl". Then,
3.  Results:
4.  Conclusion:

```{r echo=FALSE, warning=FALSE, message=FALSE}
# part b

annoyed <- nbc |>
  filter(Show %in% c("The Biggest Loser", "The Apprentice: Los Angeles"))

boot_annoyed <- do(10000) * mean(~Q1_Annoyed, data = mosaic::resample(annoyed))

boot_annoyed |>
  summarize(std_err_ = sd(mean))

ggplot(boot_annoyed) + 
  geom_histogram(aes(x= mean))

confint(boot_annoyed, level=0.95)
```

## Part B

1.  Question: Which reality contest made people feel more annoyed: "The Biggest Loser" or "The Apprentice: Los Angeles"
2.  Approach: To answer this question, I used viewer responses from the dataset for two shows called "The Biggest Loser" and "The Apprentice: Los Angeles". Then,
3.  Results:
4.  Conclusion:

```{r echo=FALSE, warning=FALSE, message=FALSE}
# part c

confusing <- nbc |>
  filter(Show == "Dancing with the Stars")

boot_confusing <- do(10000) * mean(~Q2_Confusing, data = mosaic::resample(confusing))

boot_confusing |>
  summarize(std_err_ = sd(mean))

ggplot(boot_confusing) + 
  geom_histogram(aes(x= mean))

confint(boot_confusing, level=0.95)
```

## Part C

1.  Question: Is the premise of "Dancing with the Stars" confusing?
2.  Approach: To answer this question, I used viewer responses from the dataset for the show "Dancing with the Stars". Then,
3.  Results:
4.  Conclusion:

# Problem 4

```{r echo=FALSE}
# q4


```

1.  Question:
2.  Approach:
3.  Results:
4.  Conclusion:
